Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-24 paper/paper.qmd
updated

---
title: "Tornto annual energy consumption"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption"
author: 
  - Irene Liu
thanks: "Code and data are available at: https://github.com/zilin1017/Toronto_annual_energy_consumption.git."
date: today
date-format: long
abstract: "This study examines the relationship between building size(GFA) and electricity consumption in Toronto's public facilities. Data from over 500 buildings, including schools,libraries, and hospitals, show a consistent positive correlation between GFA and eletricity usage. Larger facilities, particularly healthcare centers, demonstrate higher energy consumption per square meter. These results help inform efforts to improve energy management in Toronto’s public buildings."
format: pdf
number-sections: true
bibliography: references.bib
---
